### 2014-06-19 ms/ms.Rmd
Fix author initials. Closes #120

We (D. Falster and R.A. Duursma, with the help of D. Barneche, R. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by Daniel Falster and Remko Duursma. Diego Barneche, Rich FitzJohn and Angelica Vårhammar assisted with literature searching, data compilation, and coding. A separate compilation focussing on natural forests in Japan, was collected by Masae Ishihara, with assistance from Tsutom Hiura, Hajime Utsugi and Hiroyuki Tanouchi. All other authors contributed data to the project.

@@

D.S. Falster, A. Vårhammer and D. R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R FitzJohn was employed on a XXXXXX.

>>>>

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by D.S. Falster and R.A. Duursma. D.R. Barneche, R.G. FitzJohn and A. Vårhammar assisted with literature searching, data compilation, and coding. A separate compilation focussing on natural forests in Japan, was collected by M. Ishihara, with assistance from T. Hiura, H. Utsugi and H. Tanouchi. All other authors contributed data to the project.

@@

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174).
